---
title: "analysis-template"
author: "Emeline"
date: "DD/MM/YYYY"
output: html_document
---
# Copyright 2021 Emeline Favreau, University College London.

This template allows you to analyse data, create figures and make a html or pdf report to share with your collaborators.

# General notes about this template for readable source code
- Good and consistent formatting, with indentations and functions without too many arguments
- Good and consistent naming, such as CamelCase or Snake_
- Accurate comments on implentation decisions, names of algorithms, expected format of input files
- Appropriate coding convention: add a copyright, include R version, use Codetools (check R code for possible problems)
- If new function, use roxygen2 to automate documentation

# Learn more:
- R Markdown: https://rmarkdown.rstudio.com/authoring_basics.html
- Writing readable source code: https://software.ac.uk/resources/guides/writing-readable-source-code
- R style convention: http://adv-r.had.co.nz/Style.html
- codetools: https://cran.r-project.org/web/packages/codetools/index.html
- roxygen2: https://github.com/r-lib/roxygen2

---
# Objective of analysis
Making a small graph for my brother's podcast view data.


## Analysis steps:
- Obtaining data
- Aim 1: description
- Aim 2: description
- Aim 3: description
- Aim 4: description



```{r load all the libraries, eval = TRUE, echo = FALSE, include = FALSE}
# get libraries
basic_libraries <- c("ggplot2",
                     "tidyverse",
                     "data.table")
for (lib in basic_libraries) {
        if (require(package = lib, character.only = TRUE)) {
                print("Successful")
        } else {
                print("Installing")
                install.packages(lib)
                library(lib, character.only = TRUE )
        }
}
```

```{r import data, eval = TRUE, echo = FALSE, include = FALSE}
# add all the files needed here, with descriptions
# file obtained by tool/person, containing data description
# expected format of input files


# each podcast episode has a number of listens
# column one: number of listens (e.g 331 listens for episode 0 of series 1)
podcast_data <- fread('https://lecridelagirafe.org/log-qmpp/total.txt')

# check the data
head(podcast_data)

# check that listens (column 1) are interger
str(podcast_data)


```

## Aim 1: make a small plot 

```{r aim 1, eval = TRUE, echo = FALSE, include = TRUE}
# add column names
colnames(podcast_data) <- c("num_listens", "episode_name")

# the first episode came out: 30 juin 2021 (on a wednesday)
s01e00_date <- as.Date("2021-06-30")

# each episode came out on a wednesday
# add a column for number of days since episode is online

# initiate the column date with dummy data
podcast_data$date <- s01e00_date

# for each row, starting on the second row  
for(num_row in 2:nrow(podcast_data)){
  podcast_data$date[num_row] <- podcast_data$date[num_row - 1] +7
}

# add a column for cumulated days since the episode is online
podcast_data$live_day_num <- as.numeric(Sys.Date() - podcast_data$date)


# make a figure 
# x axis: number of days since the episode is online
# y axis: number of listens (cumulated)
# https://www.r-graph-gallery.com/274-map-a-variable-to-ggplot2-scatterplot.html
ggplot(podcast_data,
       aes(x=live_day_num,
           y=num_listens,
           color=episode_name)) + 
    geom_point(size=3) +
  theme_bw()



```

Conclusion

## Aim 2: description

```{r aim 2, eval = TRUE, echo = FALSE, include = TRUE}
# perform analysis 
# make a figure 
```

Conclusion

## Aim 3: description

```{r aim 3, eval = TRUE, echo = FALSE, include = TRUE}
# perform analysis 
# make a figure 
```

Conclusion

## Aim 4: description

```{r aim 4, eval = TRUE, echo = FALSE, include = TRUE}
# perform analysis 
# make a figure 
```

Conclusion


```{r record versions of session, eval = TRUE, echo = FALSE, include = FALSE}
# record versions of R and packages here
sessionInfo()
# R version 3.6.3 (2020-02-29)
# Platform: x86_64-apple-darwin15.6.0 (64-bit)
# Running under: macOS Catalina 10.15.4
# 
# Matrix products: default
# BLAS:   /System/Library/Frameworks/Accelerate.framework/Versions/A/Frameworks/vecLib.framework/Versions/A/libBLAS.dylib
# LAPACK: /Library/Frameworks/R.framework/Versions/3.6/Resources/lib/libRlapack.dylib
# 
# locale:
# [1] en_GB.UTF-8/en_GB.UTF-8/en_GB.UTF-8/C/en_GB.UTF-8/en_GB.UTF-8
# 
# attached base packages:
# [1] stats     graphics  grDevices utils     datasets  methods   base     
# 
# other attached packages:
# [1] forcats_0.5.0   stringr_1.4.0   dplyr_0.8.5     purrr_0.3.4     readr_1.3.1    
# [6] tidyr_1.0.3     tibble_3.0.1    tidyverse_1.3.0 ggplot2_3.3.0  
# loaded via a namespace (and not attached):
#  [1] Rcpp_1.0.4.6     cellranger_1.1.0 pillar_1.4.4     compiler_3.6.3   dbplyr_1.4.3    
#  [6] tools_3.6.3      lubridate_1.7.8  jsonlite_1.6.1   lifecycle_0.2.0  gtable_0.3.0    
# [11] nlme_3.1-147     lattice_0.20-41  pkgconfig_2.0.3  rlang_0.4.6      reprex_0.3.0    
# [16] cli_2.0.2        DBI_1.1.0        rstudioapi_0.11  yaml_2.2.1       haven_2.2.0     
# [21] xfun_0.13        xml2_1.3.2       withr_2.2.0      httr_1.4.1       knitr_1.28      
# [26] fs_1.4.1         generics_0.0.2   vctrs_0.3.0      hms_0.5.3        grid_3.6.3      
# [31] tidyselect_1.1.0 glue_1.4.1       R6_2.4.1         fansi_0.4.1      readxl_1.3.1    
# [36] modelr_0.1.7     magrittr_1.5     scales_1.1.1     backports_1.1.7  ellipsis_0.3.0  
# [41] rvest_0.3.5      assertthat_0.2.1 colorspace_1.4-1 stringi_1.4.6    munsell_0.5.0   
# [46] broom_0.5.6      crayon_1.3.4 
```